### 2017-01-31 analysis-note-vf/results.tex
update the note and the coherent paper with the latest plots

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_phi.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The blue error bars 
   represent the statistical and the systematic uncertainties, added 
   quadratically, shown on the top of green error bars representing only the 
statistical uncertainties.  The brown bands represent the full systematic 
uncertainties, including the normalisation systematic uncertainties. The red 
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:bsa_coh_Q2_bins}
\end{figure}

@@

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_Q2_shortscenrario.pdf}\\ 
\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_x_shortscenrario.pdf}\\
\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_t_shortscenrario.pdf} \\ 
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
   the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle 
   panel: the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
   $-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
   the colored curves represent theoretical calculations from 
\cite{simonetta_2}.  } \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (black full squares 
in the top panel plots) and real (empty black squares in the bottom panel 
plots) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of $Q^{2}$ (on the 
left), $x_B$ (on the middle), and $t$ (on the right). The full and dashed red 
curves are calculations based on the impulse approximation from 
\cite{Vadim_priv}.  The black curves in the right plots, t-dependence plots, 
are calculations from a convolution model based on the VGG model for the 
nucleon's GPDs \cite{Guidal_priv}. The cyan curve on the top-right plot is from 
the off-shell calculations presented in section \ref{Theoretical_hypotheses} 
based on reference \cite{GonzalezHernandez:2012jv}.  }
\label{fig:HA_CFF}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results, the 
   green circles are the HERMES inclusive measurement \cite{HERMES_BSA} 
   results.  The blue and red curves are from an on-shell calculations from S.  
Liuti and K. Taneja \cite{simonetta_2}. The solid and dashed black curves are 
from the off-shell calculations \cite{EMC_vadim_2}.} 
\label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.85]{fig_Dec2016/Coherent_ALU_phi.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The black error bars 
   represent the statistical uncertainties. The bluish-gray bands represent the 
systematic uncertainties, including the normalisation systematic uncertainties.  
The red curves represent fits, in the form of equation \ref{eq:A_LU-coh}, for 
the asymmetries with the statistical and the systematic uncertainties added   
quadratically.}
\label{fig:bsa_coh_Q2_bins}
\end{figure}

@@

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.52]{fig_Dec2016/ALU_90_p_vs_Q2_shortscenrario.pdf}\\ 
\includegraphics[scale=0.52]{fig_Dec2016/ALU_90_p_vs_x_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{fig_Dec2016/ALU_90_p_vs_t_shortscenrario.pdf} \\ 
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
   the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle 
   panel: the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
   $-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
   the colored curves represent theoretical calculations from 
\cite{simonetta_2}.  } \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[scale=0.8]{fig_Dec2016/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (black full squares 
in the top panel plots) and real (empty black squares in the bottom panel 
plots) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of $Q^{2}$ (on the 
left), $x_B$ (on the middle), and $t$ (on the right). The full red curves are 
calculations based on the impulse approximation from \cite{Vadim_priv}.  The 
black dashed curves are calculations from a convolution model based on the VGG 
model for the nucleon's GPDs \cite{Guidal_priv}. The blue long-dashed curve on 
the top-right plot is from the off-shell calculations presented in section 
\ref{Theoretical_hypotheses} based on reference 
\cite{GonzalezHernandez:2012jv}.  }
\label{fig:HA_CFF}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.52]{fig_Dec2016/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{fig_Dec2016/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{fig_Dec2016/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results, the 
   green circles are the HERMES inclusive measurement \cite{HERMES_BSA} 
   results.  The blue and red curves are from an on-shell calculations from S.  
Liuti and K. Taneja \cite{simonetta_2}. The solid and dashed black curves are 
from the off-shell calculations \cite{EMC_vadim_2}.} 
\label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
